An IFS study of Low-powered Radio Galaxies

### 2019-11-03 paper.tex
Further work on corrections from Martin

% \usepackage[flushleft, referable]{threeparttablex} % Adding notes under tables
\usepackage[version=4]{mhchem} 	% typeset chemistry symbols
\usepackage{array} % For wrapping text in cell in tables with multicolumntype
% \usepackage{pdflscape} % for landscape pages

@@

% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
\author[J. Warren et al.]{
  Joshua Warren,$^{1}$\thanks{Contact e-mail:
    \href{mailto:warrenj@gmx.com}{warrenj@gmx.com}}
%Joshua Warren,$^{1}$\thanks{Contact e-mail: \href{mailto:joshua.warren@physics.ox.ac.uk}{joshua.warren@physics.ox.ac.uk}}
  Martin Bureau,$^{1,2}$ Bernd Hasemann,$^{3}$ Isabella
  Prandoni,$^{4}$ \newauthor Francesco Santoro,$^{4}$ Robert
  Laing,$^{4}$ Paola Parma,$^{4}$ Hans de Ruiter$^{4}$ and \newauthor
  Arturo Mignano$^{4}$
  \\
  $^{1}$Sub-department of Astrophysics, Department of Physics,
  University of Oxford, Denys Wilkinson Building, Keble Road, Oxford
  OX1 3RH, UK\\
  $^{2}$Yonsei Frontier Lab and Department of Astronomy, Yonsei
  University, 50 Yonsei-ro, Seodaemun-gu, Seoul 03722, Republic of
  Korea\\
  $^{3}$European Southern Observatory, Karl-Schwarzschild-Str.\ 2,
  85748 Garching b.\ M{\"u}nchen, Germany\\
  $^{4}$INAF - Istituto di Radioastronomia, Via P.\ Gobetti 101, 40129
  Bologna, Italy\\
  $^*${\bf Should you/we add Ilaria Ruffa and/or Rosita Paladino
    and/or Timothy Davis as authors (they are all on the first/ALMA
    paper)?}\\{\bf I feel it is a little strange that Ilaria is not (so I
    would argue we should add her), I am much less sure about
    Rosita,}\\ {\bf and I suspect it is ok that Tim is not. Your call
    though. Also needed are updated affiliations for Francesco and
    Robert.}}

@@

We note that for the MUSE observations of NGC~1316, the NaD absorption
feature (generally attributed to absorption from the galaxy ISM and
thus affected by the ISM kinematics) was significantly affecting the
quality of the best-fitting {\bf (Spatially-collapsed? Clarify.)}
stellar spectrum. For this reason, when fitting the stellar spectra
only {\bf (i.e.\ Sections~\ref{subsec:starKin} and
  \ref{subsec:absorption} but not \ref{subsec:EmissionLines}?
  Clarify.)}, the wavelength range of the NGC~1316 spectra was
restricted to $<5800$~\AA.

@@

In this analysis we consider the following emission lines and
doublets: H$\gamma$, H$\beta$,
[\ion{O}{iii}]$\lambda\lambda$4969,5007,
[\ion{N}{I}]$\lambda\lambda$5199,5202,
[\ion{O}{i}]$\lambda\lambda$6300,6363,
[\ion{N}{ii}]$\lambda\lambda$6548,6583, H$\alpha$ and
[\ion{S}{ii}]$\lambda\lambda$6716,6731 {\bf (Should the \ion{O}{ii}
  doublet discussed a few lines below also be quoted here? Or should
  the below be the \ion{O}{i} or \ion{O}{iii} doublet already quoted?
  What about H$\delta$, also in your original table but now commented
  out? Correct.)}. We fit the emission line fluxes and kinematics
independently of the stellar kinematics, and their fluxes
independently of each other (but see below), again adopting a single
Gaussian template parametrised by $V$, the mean velocity, and
$\sigma$, the velocity dispersion for all lines. However, in the cases
of the [\ion{O}{iii}], [\ion{O}{i}] and [\ion{N}{ii}] doublets, the
two components of each doublet are fit with a fixed flux ratio of
$3:1$, while the [\ion{N}{i}] doublet is fit with a fixed flux ratio
of $3:2$ \citep{Safier1992}. The two components of the [\ion{O}{ii}]
and [\ion{S}{ii}] doublets are fit independently {\bf (See previous
  comment about the \ion{O}{ii} doublet. Correct.)}. To minimise
template mismatch, whereby emission lines are erroneously fitted to
the edges of badly modelled and thus subtracted absorption features,
we follow the procedure set out in \citet{Sarzi2005}. In this method,
the stellar component is first fitted as above with potential emission
line regions masked, followed by the unmasking and fitting of the
[\ion{O}{iii}] doublet (that sets the kinematics of all other emission
lines), and finally the fitting of the amplitudes of the remaining
emission lines.

@@

The line strengths quoted are corrected for both line emission and the
effects of the stellar velocity dispersion, as detailed below.

\subsubsection{Removing Emission Lines}
\label{subsubsec:RemovingEmission}

Each emission line is removed from each spectrum by subtracting the
best-fitting Gaussian from Section~\ref{subsec:EmissionLines} from the
data, using only the stellar templates (and continuum correction)
subsequently considered for the velocity dispersion correction (see
below). {\bf (I do not understand the second part of this
  sentence. Check/clarify/correct.)}
% used for reconstructing the best-fit to

>>>>

% \usepackage[flushleft, referable]{threeparttablex} % Adding notes under tables
\usepackage[version=4]{mhchem} 	% typeset chemistry symbols
\usepackage{array} % For wrapping text in cell in tables with multicolumntype
% \usepackage{pdflscape} % for landscape pages
\usepackage{color,soul} % highlighting
\DeclareRobustCommand{\removed}[1]{{\sethlcolor{red}\hl{#1}}}
\DeclareRobustCommand{\added}[1]{{\sethlcolor{green}\hl{#1}}}

\soulregister\cite7
\soulregister\citep7
\soulregister\citet7
\soulregister\citealt7
\soulregister\ref7
\soulregister\textbf7
\soulregister\ 7
\soulregister\ion7
\soulregister\subsubsection7
\soulregister\subsubsection1

@@

% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
\author[J. Warren et al.]{
  Joshua Warren,$^{1}$\thanks{Contact e-mail:
    \href{mailto:warrenj@gmx.com}{warrenj@gmx.com}}
%Joshua Warren,$^{1}$\thanks{Contact e-mail: \href{mailto:joshua.warren@physics.ox.ac.uk}{joshua.warren@physics.ox.ac.uk}}
  Martin Bureau,$^{1,2}$ Bernd Hasemann,$^{3}$ \added{Ilaria Ruffa,$^{4}$} Isabella
  Prandoni,$^{4}$ \newauthor Francesco Santoro,$^{4}$ Robert
  Laing,$^{4}$ Paola Parma,$^{4}$ \added{Rosita Paladino,$^{4}$} Hans de Ruiter,$^{4}$ \newauthor
  Arturo Mignano$^{4}$ and \added{Timothy Davis$^{5}$}
  \\
  $^{1}$Sub-department of Astrophysics, Department of Physics,
  University of Oxford, Denys Wilkinson Building, Keble Road, Oxford
  OX1 3RH, UK\\
  $^{2}$Yonsei Frontier Lab and Department of Astronomy, Yonsei
  University, 50 Yonsei-ro, Seodaemun-gu, Seoul 03722, Republic of
  Korea\\
  $^{3}$European Southern Observatory, Karl-Schwarzschild-Str.\ 2,
  85748 Garching b.\ M{\"u}nchen, Germany\\
  $^{4}$INAF - Istituto di Radioastronomia, Via P.\ Gobetti 101, 40129
  Bologna, Italy\\
  \added{$^{5}$School of Physics \& Astronomy, Cardiff University, Queens Buildings, The Parade, Cardiff CF24 3AA, UK}\\
  $^*${\bf Should you/we add Ilaria Ruffa and/or Rosita Paladino
    and/or Timothy Davis as authors (they are all on the first/ALMA
    paper)?}\\{\bf I feel it is a little strange that Ilaria is not (so I
    would argue we should add her), I am much less sure about
    Rosita,}\\ {\bf and I suspect it is ok that Tim is not. Your call
    though. Also needed are updated affiliations for Francesco and
    Robert.}}

@@

We note that for the MUSE observations of NGC~1316, the NaD absorption
feature (generally attributed to absorption from the galaxy ISM and
thus affected by the ISM kinematics) was significantly affecting the
quality of the \removed{best-fitting \textbf{(Spatially-collapsed? 
Clarify.)} stellar spectrum} \added{fits to the stellar 
spectrum for all bins}. For this reason, when fitting the stellar spectra
only {\bf (i.e.\ Sections~\ref{subsec:starKin} and
  \ref{subsec:absorption} but not \ref{subsec:EmissionLines}?
  Clarify.)}} \added{(i.e.\ Sections~\ref{subsec:starKin})}, the wavelength range of the NGC~1316 spectra was
restricted to $<5800$~\AA. \added{The best-fitting stellar spectra were then extrapolated above 5800~\AA.}

% Bit more detail needed above****************************************************************************************************************************************************************

@@

In this analysis, we consider the following emission lines and
doublets: 
\added{[\ion{O}{II}]$\lambda\lambda$3726,3729,
H$\delta$,} H$\gamma$, H$\beta$,
[\ion{O}{iii}]$\lambda\lambda$4969,5007,
[\ion{N}{I}]$\lambda\lambda$5199,5202,
[\ion{O}{i}]$\lambda\lambda$6300,6363,
[\ion{N}{ii}]$\lambda\lambda$6548,6583, H$\alpha$ and
[\ion{S}{ii}]$\lambda\lambda$6716,6731 {\bf (Should the \ion{O}{ii}
  doublet discussed a few lines below also be quoted here? Or should
  the below be the \ion{O}{i} or \ion{O}{iii} doublet already quoted?
  What about H$\delta$, also in your original table but now commented
  out? Correct.)}. \removed{We fit the emission line fluxes and kinematics
independently of the stellar kinematics, and their fluxes
independently of each other (but see below).} To minimise template 
mismatch, whereby emission lines are erroneously fitted
to the edges of badly modelled and thus subtracted absorption features,
we follow the procedure set out in \citet{Sarzi2005}. In this method,
the stellar component is first fitted as above with potential emission
line regions masked, followed by the unmasking and fitting of the
[\ion{O}{iii}] doublet, again adopting a single
Gaussian template parametrised by $V$, the mean velocity, and
$\sigma$, the velocity dispersion. Setting this as the kinematics for 
all other emission lines, the amplitudes of the remaining
emission lines are fitted. In the cases of the [\ion{O}{iii}], [\ion{O}{i}] 
and [\ion{N}{ii}] doublets, the two components of each doublet are fit 
with a fixed flux ratio of $3:1$, while the [\ion{N}{i}] doublet is 
fit with a fixed flux ratio of $3:2$ \citep{Safier1992}. The two 
components of the [\ion{O}{ii}] and [\ion{S}{ii}] doublets are fit 
independently. {\bf (See previous comment about the \ion{O}{ii} doublet. 
Correct.)}.

@@

\removed{\subsubsection{Removing Emission Lines}}
% \label{subsubsec:RemovingEmission}

Each emission line is removed from each spectrum by subtracting the
best-fitting Gaussians from Section~\ref{subsec:EmissionLines} from the
data, before the line strenghts are measured. \removed{, using only the 
stellar templates (and continuum correction) subsequently considered 
for the velocity dispersion correction (see below). \mbox{\textbf{(I do not 
understand the second part of this sentence. Check/clarify/correct.)}}} 
These are then corrected for the effects of the stellar velocity 
dispersion, as detailed below.
% used for reconstructing the best-fit to
